---
title: "two-parameters"
author: "Ronit Dash"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
nhanes |> filter(sex == "Male", age >= +18) |> select(height) |> drop_na() |>
ggplot(aes(x = height)) + geom_histogram(bins = 50) + 
labs(title = "Male Adult Height in the US in 2010",
x = "Height(cm)", y = "Count", 
caption = "Source: National Health and Nutrition Examination Survey")
```

Using the results of a National Health and Nutrition and Examination Survey from 2009-2011, we are analyzing and creating a model for the average height of adult men in America. One issue could be that males may have immigrated into America that skew the average height. We used an intercept-only regression to model height. The average height of adult men in America is 176 cm, with a confidence interval of 172-180.

```{r}
#| cache: TRUE
fit_male_height <- brm(formula = height ~ 1, data = nhanes, family = gaussian(), 
silent = 2, 
refresh = 0, 
seed = 12)
```

```{r}
tbl_regression(fit_male_height, intercept = TRUE)
ndata <- tibble(.rows = 1)
```

```{r}
#| label: plot
fit_male_height |> add_predicted_draws(newdata = ndata) |>
ggplot(aes(x = .prediction)) + 
geom_histogram(aes(y = after_stat(count / sum(count))), bins = 100) + 
labs(title = "Posterior for Height of Random Male", 
subtitle = "Uncertainty for a single individual is much greater than for the expected value", 
x = "Height(cm)", y = "Probability", 
caption = "Data source: NHANES") + scale_x_continuous(labels = scales::number_format()) +
scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}
fit_male_height |> add_predicted_draws(newdata = ndata) |>
mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |>
summarize(odds = mean(tall))
```
